Model definition

### 2025-05-24 nbs/tutorials/models.qmd
docs(models): enable execution
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

```python
import torch
import pyro
import numpy as np
import matplotlib.pyplot as plt
import scanpy as sc
import scvelo as scv
from pyrovelocity.utils import print_anndata, anndata_string, print_string_diff
from pyrovelocity.models.modular import PyroVelocityModel
from pyrovelocity.models.modular.factory import create_legacy_model2
from pyrovelocity.io.datasets import bifurcation_14

@@

```python
from pyrovelocity.models.modular.registry import (
    DynamicsModelRegistry,
    PriorModelRegistry,
    LikelihoodModelRegistry,
    ObservationModelRegistry,
    InferenceGuideRegistry
)
from pyrovelocity.models.modular.model import PyroVelocityModel

@@

```python
from pyrovelocity.models.modular.factory import (
    create_model_from_config,
    create_legacy_model1,
    create_legacy_model2
)
from pyrovelocity.models.modular.config import ModelConfig

@@

```python
import matplotlib.pyplot as plt

@@

# Set up the plot
fig, axes = plt.subplots(1, 2, figsize=(12, 5))

# Plot 1: Primary legacy model (create_legacy_model2)
scv.pl.velocity_embedding_grid(
    adata_with_velocity,
    basis='umap',
    color='leiden',
    title='PyroVelocity Legacy Model 2 (add_offset=True)',
    vkey='velocity_legacy2',  # Use the velocity key added by get_velocity
    s=15,
    alpha=1,
    linewidth=0.5,
    ax=axes[0],
    show=False,
    legend_loc='right margin',
    density=0.4,
    scale=0.2,
    arrow_size=2,
    arrow_length=2,
    arrow_color='black',
)

# Plot 2: Alternative model comparison (if computed)
if 'velocity_primary_legacy2' in adata_primary.layers:
    scv.pl.velocity_embedding_grid(
        adata_primary,
        basis='umap',
        color='leiden',
        title='PyroVelocity Primary Legacy Model',
        vkey='velocity_primary_legacy2',
        s=15,
        alpha=1,
        linewidth=0.5,
        ax=axes[1],
        show=False,
        legend_loc='right margin',
        density=0.4,
        scale=0.2,
        arrow_size=2,
        arrow_length=2,
        arrow_color='black',
    )
else:
    axes[1].text(0.5, 0.5, 'Alternative model\nnot computed',
                ha='center', va='center', transform=axes[1].transAxes)
    axes[1].axis('off')

>>>>

```{python}
import torch
import pyro
import numpy as np
import matplotlib.pyplot as plt
import scanpy as sc
import scvelo as scv
from pyrovelocity.utils import print_anndata, anndata_string, print_string_diff
from pyrovelocity.models.modular import PyroVelocityModel
from pyrovelocity.models.modular.factory import create_legacy_model2
from pyrovelocity.io.datasets import bifurcation_14

@@

```{python}
from pyrovelocity.models.modular.registry import (
    DynamicsModelRegistry,
    PriorModelRegistry,
    LikelihoodModelRegistry,
    ObservationModelRegistry,
    InferenceGuideRegistry
)
from pyrovelocity.models.modular.model import PyroVelocityModel

@@

```{python}
from pyrovelocity.models.modular.factory import (
    create_model_from_config,
    create_legacy_model1,
    create_legacy_model2
)
from pyrovelocity.models.modular.config import ModelConfig

@@

```{python}
import matplotlib.pyplot as plt

@@

# Set up the plot
fig, axes = plt.subplots()

# Plot 1: Primary legacy model (create_legacy_model2)
scv.pl.velocity_embedding_grid(
    adata_with_velocity,
    basis='umap',
    color='leiden',
    title='PyroVelocity Legacy Model 2 (add_offset=True)',
    vkey='velocity_legacy2',  # Use the velocity key added by get_velocity
    s=15,
    alpha=1,
    linewidth=0.5,
    ax=axes,
    show=False,
    legend_loc='right margin',
    density=0.4,
    scale=0.2,
    arrow_size=2,
    arrow_length=2,
    arrow_color='black',
)
